### 2021-06-05 paper/report.tex
Fix mistyped command.

\section{Main contributions}

\begin{itemize}
    \item Pattern: Large 2nd/3rd waves, B.1.1.7 dominant variant, steep fall in spring
    \item Many policies and developments at once: Seasonality, NPIs (private / school closures / workplace restrictions), , vaccinations, tests.
    \item Model that makes the most of many available data sources to gauge the relative effects in this transition period -- see joint distribution of infections with age, geography. But contacts with age, geography, occupations.
    \item Intuitive -- directly work with primitives
    \item Very general approach: Limited only by size of computer and availability of data
    \item Too many policies at once for SEIR extensions
\end{itemize}

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We start our analysis in mid-September for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were traced to international travel,\comment[id=HM]{citation?} which is not part of this model.

We describe the evolution of the pandemic and of its drivers in Figure~\ref{fig:pandemic_drivers_model_fit}. The black line in Figure~\ref{fig:aggregated_fit} shows the officially recorded cases; the \replace[id=HM]{color} line in

>>>>

@@

Model that makes the most of many available data sources to gauge the relative effects in this transition period -- see joint distribution of infections with age, geography. But contacts with age, geography, occupations.

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We start our analysis in mid-September for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were traced to international travel,\comment[id=HM]{citation?}, but the precise number is difficult to model.

At the starting point of our analysis, the

The \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}. The Figure~\ref{fig:stringency_index}

We describe the evolution of the pandemic and of its drivers in Figure~\ref{fig:pandemic_drivers_model_fit}. The black line in Figure~\ref{fig:aggregated_fit} shows the officially recorded cases;

We transform the index so that 1 represents the situation in mid-September and 0 represents that all restrictions incorporated in the index are in place. The six weeks between  was a steep rise in infections in
